Chasing \rainbows{} with the Habitable Worlds Observatory

### 2023-03-07 src/tex/ms.tex
[showyourwork] overleaf sync

\begin{figure}
   \centering
   \includegraphics[width=0.99\columnwidth]{figures/ellipse.pdf}
   \caption{
  Ellipse drawingIf you agree that this makes sense, I could try to add this to the yarn ball script by Matt?    }
    \label{fig:ellipse}
%    \script{plot-orb-grid.py}
\end{figure}

@@

\begin{figure*}
    \centering
    \includegraphics[width=0.6\textwidth]{figures/features_plot_peak.png}  
    \caption{
        Number of systems vs inner working angle
    }
    \label{fig:accessible_phase_angles}
\end{figure*}

>>>>

\begin{figure}
   \centering
   \includegraphics[width=0.99\columnwidth]{figures/ellipse.pdf}
   \caption{
  Ellipse drawingIf you agree that this makes sense, I could try to add this to the yarn ball script by Matt? \todo{sophia: I have posted code in the slack to calculate beta min-max for randomly orientated eccentric orbits. I don't know how to add it to the code we already have.}}
    \label{fig:ellipse}
%    \script{plot-orb-grid.py}
\end{figure}

@@

%\begin{figure*}
%    \centering
%    \includegraphics[width=0.6\textwidth]{figures/features_plot_peak.png}  
%    \caption{
%        Number of systems vs inner working angle
%    }
%    \label{fig:accessible_phase_angles}
%\end{figure*}

\begin{figure*}
    \centering
    \includegraphics[width=0.95\textwidth]{figures/nplanets_vs_iwa.png}  
    \caption{
        Number of systems vs inner working angle
    }
    \label{fig:accessible_phase_angles}
    \script{plot_features_vs_iwa.py}
\end{figure*}

\begin{figure*}
    \centering
    \includegraphics[width=0.95\textwidth]{figures/accessible_phase_angles.png}  
    \caption{
        The big kahuna
    }
    \label{fig:betaallofit}
    \script{plot_n_versus_phase.py}
\end{figure*}
